Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-08-08 paper/ms.tex
More work in prep for submission. Added Jared as an author.

\received{June 1, 2019}
\revised{January 10, 2019}
\accepted{\today}

@@

@@

This work was supported in part by the U.S.\ Department of Energy under
grant DE-FG02-87ER40317 and in part by the U.S.\ National Science Foundation
via a supplement to grant AST-1211563.
Support also came from the Data + Computing = Discovery summer program at
the Institute for Advanced Computational Science at Stony Brook University.
The software used in this work was developed in part by the DOE-supported
ASC/Alliances Center for Astrophysical Thermonuclear Flashes at the
University of Chicago. The authors gratefully thank Josiah 
Schwab and Jared Brooks for providing the hybrid progenitor models 
used in this study and for comments on the manuscript. This study would 
not have been possible without their kind help. The authors also
thank Peter Hoeflich for very helpful discussions of this and related work. 
The source code used for
this study is available as a package compatible with the
current \FLASH\ code from \url{http://astronomy.ua.edu/townsley/code.}
Results in this
paper were obtained using the high-performance computing system at the
Institute for Advanced Computational Science at Stony Brook
University.

>>>>

%\received{June 1, 2019}
%\revised{January 10, 2019}
%\accepted{\today}

@@

\author{Jared Brooks}
\affiliation{
  Department of Physics \\ 
  University of California \\
  Santa Barbara, CA 93106, USA}

@@

This work was supported in part by the U.S.\ Department of Energy under
grant DE-FG02-87ER40317 and in part by the U.S.\ National Science Foundation
via a supplement to grant AST-1211563.
Support also came from the Data + Computing = Discovery summer program at
the Institute for Advanced Computational Science at Stony Brook University.
The software used in this work was developed in part by the DOE-supported
ASC/Alliances Center for Astrophysical Thermonuclear Flashes at the
University of Chicago. The authors gratefully thank Josiah 
Schwab for discussion of the study and comments on the manuscript.
not have been possible without their kind help. The authors also
thank Peter Hoeflich for very helpful discussions of this and related work. 
The source code used for
this study is available as a package compatible with the
current \FLASH\ code from \url{http://astronomy.ua.edu/townsley/code.}
Results in this
paper were obtained using the high-performance computing system at the
Institute for Advanced Computational Science at Stony Brook
University.
